Computer Science House Constitution

### 2024-08-26 constitution.tex
table of contents numbers now start at correct page number

\tableofcontents

@@

\asubsection{Expenditure Approval}
All CSH expenditures must be approved by the Financial Director and the director whose budget is going to be used for the expenditure.
Single expenditures may not exceed seventy-five dollars and Total Expenditures may not exceed one-hundred dollars.
\\* \\*
If the above amounts are to be exceeded, the expenditure must be approved by an Immediate One-Half Vote at a House Meeting before the funds may be appropriated.
At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars, but not to exceed three-hundred dollars.
A Two-Thirds Immediate Vote with twenty-five percent quorum is required to approve the purchase.
\\*\\*
For expenditures exceeding \$300 in total funding, a spending presentation must be presented at a House Meeting.
This presentation includes the funds required for the expenditure, inventory of required resources, and, if applicable, a timeline for completion.
\\* \\*
If an appropriate directorship cannot be determined for an expenditure, it is to be brought up for approval at a House Meeting as a miscellaneous expenditure and approved by an Immediate Relative Majority vote with fifty percent quorum, regardless of the amount.
This amount is to be directly subtracted from the general CSH account.
% HOUSING
\asection{Housing}

>>>>

\tableofcontents
\setcounter{page}{4}

@@

\asubsection{Expenditure Approval}
All CSH expenditures must be approved by the Financial Director and the director whose budget is going to be used for the expenditure.
Single expenditures may not exceed \$75 and Total Expenditures may not exceed \$100.
\\* \\*
If the above amounts are to be exceeded, the expenditure must be approved by an Immediate One-Half Vote at a House Meeting before the funds may be appropriated.
At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding \$100, but not to exceed \$300.
A Two-Thirds Immediate Vote with twenty-five percent quorum is required to approve the purchase.
\\*\\*
For expenditures exceeding \$300 in total funding, a spending presentation must be presented at a House Meeting.
This presentation includes the funds required for the expenditure, inventory of required resources, and, if applicable, a timeline for completion.
\\* \\*
If an appropriate directorship cannot be determined for an expenditure, it is to be brought up for approval at a House Meeting as a miscellaneous expenditure and approved by an Immediate Relative Majority vote with fifty percent quorum, regardless of the amount.
This amount is to be directly subtracted from the general CSH account.
% HOUSING
\asection{Housing}
